Understanding fine temporal scale evolutionary dynamics with lineage metrics

### 2018-04-02 paper.tex
Update on Overleaf.

In conjunction with collected fitness information, the class of a mutation (\textit{e.g.} beneficial, deleterious, or neutral) can also be tracked. Different evolutionary conditions are expected to cause different distributions of mutations along a lineage~\citep{barrick2013genome}; deviations revealed by measures of mutation accumulation can act as a barometer for unexpected evolutionary dynamics.   
The number and magnitude of deleterious mutations along a lineage can both tell us something about the ruggedness of the fitness landscape as well as how well a lineage was able to cross fitness valleys. 
Similarly, an elevated measure of neutral mutations relative to beneficial or deleterious mutations can tell us that the fitness landscape has a large neutral area that the lineage is spending most of its time drifting around.

>>>>

In conjunction with collected fitness information, the class of a mutation (\textit{e.g.} beneficial, deleterious, or neutral) can also be tracked. Different evolutionary conditions are expected to cause different distributions of mutations along a lineage~\citep{barrick2013genome}; deviations revealed by measures of mutation accumulation can act as a barometer for unexpected evolutionary dynamics.   
The number and magnitude of deleterious mutations along a lineage can both tell us something about the ruggedness of the fitness landscape as well as how well a lineage was able to cross fitness valleys~\citep{. 
Similarly, an elevated measure of neutral mutations relative to beneficial or deleterious mutations can tell us that the fitness landscape has a large neutral area that the lineage is spending most of its time drifting around.
